Manuscript results

### 2024-03-18 04_analysis/control scenarios/Erics firstline RCT/first_line_paper_survival.Rmd
updated

>>>>

```{r}
N_sim <- 100
fitted_PFS_chemo <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("exp"))
  fitted_PFS_chemo[[i]] <- fit_PFS$model.objects$models$Exponential
  print(i)
}
save(fitted_PFS_chemo, file="fitted_PFS_control_firstline_investigator_exp_100.RData")
```

### 2024-03-18 05_report/Manuscript_results_temp.Rmd
updated

```{r}
fileloc <- here::here("04_analysis","output","scenarios","basecase exp lifetime combo")
nn <- 50
```

@@

```{R}
# model results 
#res_model <- list.files(paste0(fileloc, "/Scenario 1 life-time treatment", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(here::here("04_analysis","output"), "/res_model"),full.names = TRUE)[1:5]
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[1:nn]
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount20", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount30", "/res_model"),full.names = TRUE)

@@

df_model2 <- df_model1 %>% 
  bind_rows(mutate( df_delta1, intervention = "delta")) %>% 
    mutate(Variable = factor(Variable, levels = c("LY","QALY","Cost")),
         Type = factor(Type, levels = c("LY","QALY","Total","PLGG","AE","Treatment","Radiation"))
         ) %>% 
  arrange(Variable, Type, discount, rr) %>% 
  spread(intervention, stat)

@@

# kable(tb2)
tb2a <- tb2 %>% 
  mutate(Variable = fct_recode(Variable, `Life-years` = "LY", 
                               QALY = "QALY",
                               `Total Cost` = "Total")) %>%
  #select(Variable, intervention, control, Delta , rr)
  select(Variable, intervention, control, Delta )
tb2a$Variable <- as.character(tb2a$Variable)
tb2a$Variable[tb2a$Variable=="Treatment"] <- "Targeted costs"
tb2a$Variable[tb2a$Variable=="PLGG"] <- "Non-Targeted PLGG related costs"
tb2a$Variable[tb2a$Variable=="AE"] <- "AE related costs"
tb2a$Variable[tb2a$Variable=="Radiation"] <- "Radiation costs"
tb2a$Variable <- factor(tb2a$Variable, levels = c("Life-years","QALY","Total Cost","Non-Targeted PLGG related costs",
                                                  "AE related costs","Targeted costs","Radiation costs"))
pander(tb2a)
```

```{r}
# Averaging cohort traces across simulation run
l_prop_df <- list.files(paste0(fileloc, "/trace"),full.names = TRUE)[1:nn]
prop_df  <- map_df(l_prop_df[1], readRDS) 
prop_df$cycle <- as.numeric(prop_df$cycle)
prop_df$intervention <- ifelse(prop_df$intervention == "Targeted", 1, 0)
prop_df <- apply(prop_df,2,as.numeric)
prop_df <- as.data.frame(prop_df)
prop_df <- prop_df %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
if (nn > 1) {
  for (i in 2:nn) {
    prop_df_i  <- map_df(l_prop_df[i], readRDS) 
    prop_df_i$cycle <- as.numeric(prop_df_i$cycle)
    prop_df_i$intervention <- ifelse(prop_df_i$intervention == "Targeted", 1, 0)
    prop_df_i <- prop_df_i %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
    prop_df_i <- apply(prop_df_i,2,as.numeric)
    prop_df_i <- as.data.frame(prop_df_i)
    prop_df <- prop_df + prop_df_i
  }
  prop_df <- prop_df/nn
}
prop_df$intervention <- ifelse(prop_df$intervention == 1, "Targeted", "SoC")

@@

```{r}
# AEs
l_AE_df <- list.files(paste0(fileloc, "/AE_track"),
                      full.names = TRUE)[1:nn]
AE_df <- map_df(l_AE_df[1], readRDS) 
## Targeted
AE_df_Targeted <- AE_df %>% filter(intervention == "Targeted")
AE_prop_Targeted <-apply(AE_df_Targeted %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
df_AE_Targeted <- data.frame(cycle=0:960)
df_AE_Targeted$cycle <- as.factor(df_AE_Targeted$cycle)
for (i in 1:length(AE_prop_Targeted)){
  df_AE_prop <- as.data.frame(AE_prop_Targeted[[i]])
  colnames(df_AE_prop) <- c("cycle",names(AE_prop_Targeted)[i])
  df_AE_Targeted <- df_AE_Targeted %>% left_join(df_AE_prop, by = c("cycle"))
}
df_AE_Targeted[1,-1] <- 0
df_AE_Targeted$cycle <- as.numeric(df_AE_Targeted$cycle)
df_AE_Targeted[is.na(df_AE_Targeted)] <- 0
if (nn == 1) {
  df_AE_Targeted$intervention <- "Targeted"
}

@@

df_AE <- rbind(df_AE_Targeted, df_AE_SoC)

prop_long <- df_AE %>% select(cycle,auditory,cardiovascular,neurologic,SN,stroke,visual,intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Trace Plot of PLGG-related AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "PLGG-related AE states") +
  theme_bw() +
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> a

prop_long <- df_AE %>% select(cycle,SN_gen,cardiovascular_gen,death_outside,death_SN,stroke_gen,death_cardio,death_stroke, 
                                intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Trace Plot of Other AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "Other AE states") +
  theme_bw() +
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> b
grid.arrange(a,b, nrow=2, ncol=1)
```

@@

## Supplementary Table 1

>>>>

```{r}
fileloc <- here::here("04_analysis","output","scenarios","sickkids control lnorm lifetime combo")
index <- c(1:50)
```

@@

```{R}
# model results 
#res_model <- list.files(paste0(fileloc, "/Scenario 1 life-time treatment", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(here::here("04_analysis","output"), "/res_model"),full.names = TRUE)[1:5]
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount20", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount30", "/res_model"),full.names = TRUE)

@@

df_model2 <- df_model1 %>% 
  bind_rows(mutate( df_delta1, intervention = "delta")) %>% 
    mutate(Variable = factor(Variable, levels = c("LY","QALY","Cost")),
         Type = factor(Type, levels = c("LY","QALY","Total","PLGG","AE","gen","Treatment","Radiation"))
         ) %>% 
  arrange(Variable, Type, discount, rr) %>% 
  spread(intervention, stat)

@@

# kable(tb2)
tb2a <- tb2 %>% 
  mutate(Variable = fct_recode(Variable, `Life-years` = "LY", 
                               QALY = "QALY",
                               `Total Cost` = "Total")) %>%
  #select(Variable, intervention, control, Delta , rr)
  select(Variable, intervention, control, Delta )
tb2a$Variable <- as.character(tb2a$Variable)
tb2a$Variable[tb2a$Variable=="Treatment"] <- "Targeted costs"
tb2a$Variable[tb2a$Variable=="PLGG"] <- "Non-Targeted PLGG related costs"
tb2a$Variable[tb2a$Variable=="AE"] <- "AE related costs"
tb2a$Variable[tb2a$Variable=="gen"] <- "General population costs"
tb2a$Variable[tb2a$Variable=="Radiation"] <- "Radiation costs"
tb2a$Variable <- factor(tb2a$Variable, levels = c("Life-years","QALY","Total Cost","Non-Targeted PLGG related costs",
                                                  "AE related costs" ,"General population costs", 
                                                  "Targeted costs","Radiation costs"))
pander(tb2a)
```

```{r}
# Averaging cohort traces across simulation run
l_prop_df <- list.files(paste0(fileloc, "/trace"),full.names = TRUE)[index]
prop_df  <- map_df(l_prop_df[1], readRDS) 
prop_df$cycle <- as.numeric(prop_df$cycle)
prop_df$intervention <- ifelse(prop_df$intervention == "Targeted", 1, 0)
prop_df <- apply(prop_df,2,as.numeric)
prop_df <- as.data.frame(prop_df)
prop_df <- prop_df %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
if (nn > 1) {
  for (i in 2:nn) {
    prop_df_i  <- map_df(l_prop_df[i], readRDS) 
    prop_df_i$cycle <- as.numeric(prop_df_i$cycle)
    prop_df_i$intervention <- ifelse(prop_df_i$intervention == "Targeted", 1, 0)
    prop_df_i <- prop_df_i %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
    prop_df_i <- apply(prop_df_i,2,as.numeric)
    prop_df_i <- as.data.frame(prop_df_i)
    prop_df <- prop_df + prop_df_i
  }
  prop_df <- prop_df/nn
}
prop_df$intervention <- ifelse(prop_df$intervention == 1, "Targeted", "SoC")

@@

```{r}
# AEs
l_AE_df <- list.files(paste0(fileloc, "/AE_track"),
                      full.names = TRUE)[index]
AE_df <- map_df(l_AE_df[1], readRDS) 
## Targeted
AE_df_Targeted <- AE_df %>% filter(intervention == "Targeted")
AE_prop_Targeted <-apply(AE_df_Targeted %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
df_AE_Targeted <- data.frame(cycle=0:960)
df_AE_Targeted$cycle <- as.factor(df_AE_Targeted$cycle)
for (i in 1:length(AE_prop_Targeted)){
  df_AE_prop <- as.data.frame(AE_prop_Targeted[[i]])
  colnames(df_AE_prop) <- c("cycle",names(AE_prop_Targeted)[i])
  df_AE_Targeted <- df_AE_Targeted %>% left_join(df_AE_prop, by = c("cycle"))
}
df_AE_Targeted[1,-1] <- 0
df_AE_Targeted$cycle <- as.numeric(df_AE_Targeted$cycle)
df_AE_Targeted[is.na(df_AE_Targeted)] <- 0
if (nn == 1) {
  df_AE_Targeted$intervention <- "Targeted"
}

@@

df_AE0 <- rbind(df_AE_Targeted, df_AE_SoC)
df_AE <- as.data.frame(apply(df_AE0, 2, cumsum))
df_AE$cycle <- df_AE0$cycle
df_AE$intervention <- df_AE0$intervention

prop_long <- df_AE %>% select(cycle,auditory,cardiovascular,neurologic,SN,stroke,visual,intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Cumulative Incidence of PLGG-related AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "PLGG-related AE states") +
  theme_bw() +
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> a

prop_long <- df_AE %>% select(cycle,SN_gen,cardiovascular_gen,death_outside,death_SN,stroke_gen,death_cardio,death_stroke, 
                                intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Cumulative Incidence of Other AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "Other AE states") +
  theme_bw() +
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> b
grid.arrange(a,b, nrow=2, ncol=1)
```

@@

i## Supplementary Table 1
